\sc Estimating Evolutionary Parameters for Low Complexity Regions using an Approximate Bayesian Computation

### 2023-03-13 thesis_template/paper0904.tex
Added abstract to latex paper

I want to finish the project in order to write the abstract, I want to be able to summarize everything concisely.

>>>>

It has been shown that among eukaryotic proteomes, the most commonly shared peptide sequences tend to lack stable three-dimensional structures and contain low information and entropy content. These sequences, now known as low-complexity regions, lack diversity in amino acid composition, but recent research has demonstrated an important role played by these regions in a variety of cellular functions. Model-based analysis of amino acid sequences is a common approach utilized to study molecular evolution, however, due to the increasing complexity of available data, many model-based approaches have become intractable due to difficulties in calculating the likelihood function. To overcome the issue of intractability, this study employs an approximate Bayesian computation Markov chain Monte Carlo algorithm (ABC-MCMC), which utilizes a simulation step in place of calculating the likelihood function. Through the simulation of mutated protein sequences, this study aims to investigate the evolution of protein low-complexity regions by estimating parameters such as mutation and insertion/deletion rates. This work provides insight into the formation of low-complexity regions, and demonstrates the potential of using approximate Bayesian computation methods for studying evolutionary genetics.
